Data Import & Checking

### 2019-03-16 aacr.Rmd
update

The degree of authority students attach to both automated and human feedback also is a confounding variable. Anecdotally, most instructors can cite many examples of students ignoring basic spelling and grammar feedback that is standard for word processors like MS. Word. Ruegg [@Ruegg2015] found that feedback from peer reviewers was not valued as much as teachers' feedback, even though teachers provided less explicit comments than peer reviewers. Ruegg argued that this is likely because teachers are the ones that ultimately grade the student's writing.

>>>>

The degree of authority students attach to both automated and human feedback also is a confounding variable. Anecdotally, most instructors can cite many examples of students ignoring basic spelling and grammar feedback that is standard for word processors like MS. Word. Ruegg [-@Ruegg2015] found that feedback from peer reviewers was not valued as much as teachers' feedback, even though teachers provided less explicit comments than peer reviewers. Ruegg argued that this is likely because teachers are the ones that ultimately grade the student's writing.

### 2019-03-16 background.Rmd
update

####\  
##Context & Prior Work
From prior studies (*see the Literature Review for details*), we know students make greater gains as writers if instructors avoid telling students what to correct ("copy editing"), and use a coaching-oriented approach instead [@Bazerman1994; @Bazerman2006; @Breidenbach2006; @Gottschalk2003; @Graves2011; @Kiefer2002; @NCTENWP; @Perelman2009; @Ruegg2015; @Szymanski2014;@Trupiano2006; @Underwood2006; @Anson2001; @CWPA2011; @Harris1979; @Haswell2006a; @Haswell2006b; @Reynolds2009; @Szymanski2014; @Swilky1991]. To that end, our program trains graduate TAs to use a **global issues / biggest issues first** approach to correcting undergraduate technical writing. Ideally:

>>>>

####\  
##Context & Prior Work
From prior studies (*see the Literature Review for details*), we know students make greater gains as writers if instructors avoid telling students what to correct ("copy editing"), and use a coaching-oriented approach instead [@Bazerman1994; @Bazerman2006; @Breidenbach2006; @Gottschalk2003; @Graves2011; @Kiefer2002; @NCTENWP; @Perelman2009; @Ruegg2015; @Szymanski2014; @Trupiano2006; @Underwood2006; @Anson2001; @CWPA2011; @Harris1979; @Haswell2006a; @Haswell2006b; @Reynolds2009; @Szymanski2014; @Swilky1991].

To that end, our program trains graduate TAs to use a **global issues / biggest issues first** approach to correcting undergraduate technical writing. Ideally:

### 2019-03-16 build.Rmd
update

####Extracting TAs' Comments 
*(Early coding stage)*  
Protocol used to extract TA comments from student lab reports.  
https://adanieljohnson.github.io/default_website/docxcommentextraction.html

####Structure of Development Dataset; Data Import & Validation 
*(Completed)*  
Organization of the initial dataset, and how data were imported in R and validated.  
https://adanieljohnson.github.io/default_website/dataimport.html

####Codebook for Classifying TAs' Comments 
*(Completed)*  
Describes the process for developing the codes used to classify comments.  
https://adanieljohnson.github.io/default_website/codebook.html

####Initial Exploration of the Dataset 
*(Partly completed)*  
What is the distribution of words used in the TA comments?  
https://adanieljohnson.github.io/default_website/initial_exploration.html

####Current Version of the Naive Bayes Comment Classifier 
*(Completed)*  
Code for the most recent version of the optimized NB classifier.   
https://adanieljohnson.github.io/default_website/NB_2r2c.html

####Embedding the Naive Bayes Classifier in an Ensemble Model  
*(Planning stage)*
The NB method alone does not classify TA comments with sufficient accuracy for the "Structure" category. This page outlines a vertically stacked "ensemble" classifier that uses pattern matching and other pre-processing steps to improve NB accuracy.
https://adanieljohnson.github.io/default_website/Ensemble_Notes.html

####\  
***

>>>>

####Extracting TAs' Comments 
*(Preliminary coding)*  
Fully R-based protocol for extracting TA comments from student lab reports. Will replace current process using a mix of Linux and Excel scripts.  
https://adanieljohnson.github.io/default_website/docxcommentextraction.html

####Structure of Development Dataset; Data Import & Validation 
*(Complete)*  
Organization of the initial dataset, and how data were imported in R and validated.  
https://adanieljohnson.github.io/default_website/dataimport.html

####Codebook for Classifying TAs' Comments 
*(Complete)*  
Describes the process for developing the codes used to classify comments.  
https://adanieljohnson.github.io/default_website/codebook.html

####Initial Exploration of Dataset 
*(Partly complete)*  
What is the distribution of words used in the TA comments?  
https://adanieljohnson.github.io/default_website/initial_exploration.html

####Naive Bayes Comment Classifier 
*(Complete)*  
Code for the most recent version of the optimized NB classifier.   
https://adanieljohnson.github.io/default_website/NB_2r2c.html

####Embedding Naive Bayes Classifier in an Ensemble Model  
*(Initial design stage)*
Outlines a strategy for combining pattern matching and other pre-processing steps with Naive Bayes Classifier to improve accuracy.
https://adanieljohnson.github.io/default_website/Ensemble_Notes.html

### 2019-03-16 dataimport.Rmd
update

1.  Student and TA names have been recoded using pre-assigned anonymous IDs.
2.  Vocabulary terms used in coding columns matches criteria in "codebook_for_comments.rmd"
3.  Data table headers match those listed below. The same list is in the file "code_column_names.rmd"

@@

Data were anonymized in Excel, replacing names, email addresses, and other confidential information was replaced with unique randomized alphanumeric strings **[LINK]**.

@@

Data were anonymized in Excel prior to conversion to CSV format. Names, email addresses, and other confidential information was replaced with unique randomized alphanumeric strings **[LINK]**.

@@

1.  Student and TA names have been recoded using pre-assigned anonymous IDs.
2.  Vocabulary terms used in coding columns matches criteria in "codebook_for_comments.rmd" [LINK]
3.  Data table headers match those listed below. The same list is in the file "code_column_names.rmd" [LINK]

>>>>

1.  Student and TA names have been recoded using pre-assigned anonymous IDs.
2.  Vocabulary terms used in coding columns matches comment codebook criteria described at https://adanieljohnson.github.io/default_website/codebook.html.
3.  Data table headers match those listed below.

@@

Data were anonymized in Excel, replacing names, email addresses, and other confidential information was replaced with unique randomized alphanumeric strings.

@@

Data were anonymized in Excel prior to conversion to CSV format. Names, email addresses, and other confidential information was replaced with unique randomized alphanumeric strings.

@@

1.  Student and TA names have been recoded using pre-assigned anonymous IDs.
2.  Vocabulary terms used in coding columns matches comment codebook criteria described at https://adanieljohnson.github.io/default_website/codebook.html.
3.  Data table headers match those listed below.
